### 2019-02-27 sections/abstract.tex
merge pars in abstract for better readability, also mention mTasks

% Context
Software that models how people work is omnipresent in today's society.
Current languages and frameworks often focus on usability by non-programmers, sacrificing flexibility and high level of abstraction.
Task-oriented programming (TOP) is a programming paradigm that aims to provide the desired level of abstraction while still being expressive enough to describe real world collaboration.
It prescribes a declarative programming style to specify multi-user workflows.
Workflows can be higher-order.
They communicate through typed values on a local and global level.
Such specifications can be turned into interactive applications for different platforms, supporting collaboration during execution.

% Inquiry
TOP has been around for more than a decade, in the form of iTasks, which is tailored for real-world usability.
So far, it has not been given a formalisation which is suitable for formal reasoning.

@@

% Knowledge
With TopHat we prepare a way to formally reason about TOP languages and programs.
We show some interesting properties of the language.
This approach allows for comparison with other work in the field.

% Grounding
We have implemented the semantic rules of TopHat in Idris, and the task layer on top of iTasks.
This shows that our approach is feasible, and lets us demonstrate the concepts by means of illustrative case studies.

% Importance
TOP has been employed in projects with the Dutch coast guard, tax office, and navy.
Our work matters because formal program verification is important for mission-critical software, especially for systems with concurrency.

>>>>

% Context
Software that models how people work is omnipresent in today's society.
Current languages and frameworks often focus on usability by non-programmers, sacrificing flexibility and high level abstraction.
Task-oriented programming (TOP) is a programming paradigm that aims to provide the desired level of abstraction while still being expressive enough to describe real world collaboration.
It prescribes a declarative programming style to specify multi-user workflows.
Workflows can be higher-order.
They communicate through typed values on a local and global level.
Such specifications can be turned into interactive applications for different platforms, supporting collaboration during execution.
% Inquiry
TOP has been around for more than a decade, in the forms of iTasks and mTasks, which is tailored for real-world usability.
So far, it has not been given a formalisation which is suitable for formal reasoning.

@@

% Knowledge
With TopHat we prepare a way to formally reason about TOP languages and programs.
We show some interesting properties of the language.
This approach allows for comparison with other work in the field.
% Grounding
We have implemented the semantic rules of TopHat in Idris, and the task layer on top of iTasks combinators.
This shows that our approach is feasible, and lets us demonstrate the concepts by means of illustrative case studies.
% Importance
TOP has been employed in projects with the Dutch coast guard, tax office, and navy.
Our work matters because formal program verification is important for mission-critical software, especially for systems with concurrency.
